Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-18 Documents/supplementary_text.tex
More work on supplement.

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage[font = {sf}, labelfont = {bf},
  labelsep = period, singlelinecheck = off]{caption}
\usepackage[font = {sf}]{floatrow}

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers, round, sort&compress]{natbib}
\usepackage{hypernat}

@@

\newcommand{\comment}[1]{\textbf{[#1]}}
\newcommand{\md}{\mathrm{d}}
\newcommand{\mT}{\mathrm{T}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\mat}[1]{\mathbf{#1}}
\newcommand{\me}{\mathrm{e}}

\renewcommand{\figurename}{Fig.}

@@

\begin{document}
\maketitle

\newcommand{\labelPrefix}{S}
\renewcommand{\thesection}{\labelPrefix\arabic{section}}
\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
\renewcommand{\thetable}{\labelPrefix\arabic{table}}

We developed a continuous-time, compartmental model consisting of 8
health states: susceptible to HIV infection, vaccinated against HIV,
acute HIV infection, undiagnosed HIV infection, diagnosed but
untreated HIV infection, treated without achieving viral suppression,
achieved viral suppression, and having AIDS (Supplementary text). We
found sufficient country-level demographic data, as well as estimates
of longitudinal HIV incidence and prevalence for the 15–49 age group,
spanning from as early as 1990 to 2015 to parameterize our model for
127 countries. See Supporting text for information on data sources.

Using available historical data for incidence and prevalence, and
published transmission estimates (13), we estimated transmission rates
for people with acute infection, unsuppressed viral load and
suppressed viral load. Our calibration method provided a recent
snapshot of country-specific transmission, while using historical data
to smooth out variations. See Supporting text for detailed information
on estimating the transmission rate.

@@

\section{Data sources}

@@

Our continuous-time, compartmental model consists of 8 health states:
susceptible to HIV infection, vaccinated against HIV, acute HIV
infection, undiagnosed HIV infection, diagnosed but untreated HIV
infection, treated without achieving viral suppression, achieved viral
suppression, and having AIDS (Figure \ref{model_diag}). Transitions
between states are governed by a series of differential equations
parameterized using rates estimated from other studies and from
incidence and prevalence data (Table \ref{model_param}).

\begin{table}
  \begin{center}
    \begin{tabular}{cp{4cm}llc}
      \hline
      Symbol & Definition & Value & Sampling Distribution & Source \\ \hline
      $\delta$	& Rate of leaving acute phase of HIV infection & 4.1379/year & T (4.1379, 2, 9.6) & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS among non-virally suppressed individuals
                          & 0.1064/year & & \cite{Morgan2002-cq} \\
      $\gamma$ & Rate of viral suppression & 1/year & U (0.5, 1.5) & \cite{Currie2009-yz} \\
      $\upsilon$	& Death rate from AIDS & 0.5/year &  & \cite{Morgan2002-cq} \\
      $\omega$	& Reduction in life years for treated PLHIV & 5 & U (5, 8) & \cite{Unaids2014-ue, Samji2013-kf}\\
      $\beta_{A}$	& Transmission probability during acute phase & 0.0082 & T (0.0082, 0.0039, 0.0150) & \cite{Skarbinski2015-ni,Wawer2005-us}\\
      $\beta_{U}$	& Transmission probability after acute phase & 0.0014 & T (0.0014, 0.00077, 0.00251) & \cite{Hughes2012-so}\\
      $\varepsilon$	& Proportional reduction of transmission with treatment & 0.08 & $\beta$ (0.08, 0.002, 0.57)& \cite{Donnell2010-xo}\\
      $n$			& Sex acts per year & 102 & U (96, 108) & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\ \hline
    \end{tabular}
    \caption{Parameters used in model. (T: triangular distribution, U:
      uniform distribution, $\beta$: beta distribution).}
    \label{model_param}
  \end{center}
\end{table}

The PLHIV population was comprised of people in the acutely infected,
undiagnosed, diagnosed, treated, viral suppression and AIDS
compartments. People susceptible to HIV ($S$) progress to the
acute-infection phase ($A$) according to the force of infection, which
depends on the HIV transmission rate, estimated from the
country-specific incidence and prevalence data
(\autoref{model_fitting}), adjusted for the current number of acutely
infected, untreated or ineffectively treated, and viral suppression
PLHIV.  Acute infection is characterized by high viral loads and lasts
88 [XX, YY] days \cite{Hollingsworth2008-iy}. We assumed that people
remain undiagnosed during their acute infection phase and during at
least some of the subsequent period of clinical latency (i.e., the
undiagnosed compartment). After acute infection, people move into the
chronic undiagnosed class ($U$).  People in the undiagnosed class will
be diagnosed at a rate determined by the country's initial diagnosis
level and potential progress towards the UNAIDS targets.  Diagnosed
people (compartment $D$) transition to the treated compartment ($T$)
upon starting ART at a rate of $\phi$ , and then to the
viral-suppression class ($V$) after achieving viral suppression
through treatment retention at a rate of $\gamma$. The disengagement
from treatment moves people from treated ($T$) and viral suppression
($V$) at a rate of $\omega$ back to the diagnosed class ($D$). Rates
of movement between the undiagnosed ($U$), diagnosed ($D$), treated
($T$) and viral-suppression classes ($V$) are determined by the
proportions of PLHIV diagnosed ($p_{D}$), proportion of diagnosed
people on ART ($p_{T}$), and the proportion of people on ART who have
achieved viral suppression ($p_{V}$). PLHIV in $U$, $D$, $T$, and $V$
classes develop AIDS (compartment $W$) after an average duration
dependent on viral suppression status. People who have achieved viral
suppression ($V$) take longer to develop AIDS ($1/\theta$), than those
who are in the other PLHIV classes ($1/\sigma$). People who are
susceptible to HIV are vaccinated at rate $\zeta$, transitioning into
the vaccinated compartment ($R$), where the vaccine reduces their
force of infection by the efficacy factor $\rho$.  The model equations
are
\begin{equation}
  \label{model_eqns}
  \begin{split}
    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
    \\
    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
    \\
    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
    \\
    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
    \\
    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
    - \phi D - \mu D - \sigma D,
    \\
    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
    - \sigma T,
    \\
    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
    \\
    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
    \nu W,
  \end{split}
\end{equation}
with force of infection
\begin{equation}
  \label{force_of_infection}
  \begin{split}
    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
    \\
    N &= S + R +  A + U + D + T + V,
    \\
    \beta_x &= c \left[1 - (1 - \tau_x)^n\right]
    \text{ for $x \in \{A, U, T\}$},
    \\
    \tau_T &= (1 - \epsilon) \tau_U.
  \end{split}
\end{equation}
The rate of developing AIDS among those who have acheived viral
suppression is
\begin{equation}
 \theta = \frac{1}{1/\mu-\omega-1/\nu}.
\end{equation}

The proportion diagnosed is
\begin{equation}
  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
\end{equation}
the proportion treated is
\begin{equation}
  p_T = \frac{T + V + W}{D + T + V + W},
\end{equation}
the proportion with viral suppression is
\begin{equation}
  p_V = \frac{V}{T + V},
\end{equation}
and the proportion of people vaccinated is
\begin{equation}
  P_{V} = \frac{R}{S+R}.
\end{equation}

The rates are applied when the proportions of $p_D$, $p_T$, and $p_V$
are below the target levels:
\begin{equation}
  \begin{split}
    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
    \\
    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
    \\
    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
    \\
    \zeta(t) &= \zeta_{max} H\left(P^{*}_{V}(t)-P_{V}(t)\right),
  \end{split}
\end{equation}
where $H(x)$ is the Heaviside function
\begin{equation}
  H(x) =
  \begin{cases}
    0 & \text{if $x < 0$},
    \\
    1 & \text{if $x > 0$}.
  \end{cases}
\end{equation}

@@

@@

We evaluated the global and country-specific impacts of meeting the
UNAIDS targets and vaccine deployment on four outcome measures: HIV
incidence, PLHIV, number of people with AIDS, and AIDS-related deaths
between 2015 and 2035. Calibrating our model to historical data on
prevalence and incidence, we projected the anticipated trajectories of
the outcomes using country-specific transmission rates across the
intervention scenarios outlined below.  Our base-case scenario assumed
maintenance of the status quo: that 2015 levels of the proportion of
PLHIV diagnosed ($p_{D}$), proportion of those diagnosed on ART
($p_{T}$), and proportion of those on treatment who have achieved
viral suppression ($p_{V}$) continue unchanged until 2035.  The
intervention scenarios were 1.) the attainment of the 90--90--90
target by linear increases in $p_{D}$, $p_{T}$, and $p_{V}$ until 2020
followed by maintenance of those levels until 2035, and 2.) linear
increase in the diagnosis and treatment levels to the 90--90--90
targets by 2020, a linear increase from 90--90--90 to the 95--95--95
target by 2030, and maintenance of the 95--95--95 levels to 2035. (For
90--90--90, if any initial level was above 90\%, it was kept constant
going forward so that the intervention did not worsen coverage.
Likewise, for 95--95--95, any initial level above 95\% was kept
constant.)  For vaccination, we assumed deployment of a vaccine with
50\% efficacy in 2020 with coverage increasing linearly from 0\% to
50\% at 2 years post-rollout and maintaining constant coverage after
reaching 70\%. The added benefit of vaccination was considered in the
context of status quo diagnosis and treatment, achieving the UNAIDS
90–90–90 goal by 2020 followed by maintenance, and achieving the
95–95–95 goal by 2030 followed by maintenance.  Projections were
generated through model simulations based on published parameter
distributions (\autoref{model_param}) and country-specific estimated
transmission rate distributions. The parameters were sampled using
latin hypercube sampling \cite{}
and the variance reduction technique of running different
interventions with random parameter values \cite{}.

@@

We calculated partial rank correlation coefficients (PRCC) \cite{}
to measure the independent effect of each parameter on model
projections of HIV incidence (\autoref{PRCCs}). Furthermore, due to
uncertainty surrounding the prospective vaccine, we obtained model
projections using six additional vaccine scenarios by considering
alternative estimates of efficacy (30\%, 70\%), coverage (50\%, 90\%),
speed of scale up (10\% coverage per year), and first year of
availability (2025).

>>>>

\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage{geometry}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz}

\usepackage[font = {sf}, labelfont = {bf},
  labelsep = period, singlelinecheck = off]{caption}
\usepackage[font = {sf}]{floatrow}
\usepackage{tabularx}

\usepackage[numbers, round, sort&compress]{natbib}
\renewcommand{\citenumfont}{\itshape}  % Citations get italics numbers
\makeatletter
\renewcommand\NAT@open{(\hspace*{-0.3ex}}   % Tweak spacing.
\renewcommand\@biblabel[1]{#1.}  % Reference list doesn't use square brackets.
\makeatother

@@

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{hypernat}

\newcommand{\comment}[1]{\textbf{[#1]}}
\newcommand{\md}{\mathrm{d}}
\newcommand{\mT}{\mathrm{T}}
\renewcommand{\vec}[1]{\mathbf{#1}}
\newcommand{\mat}[1]{\mathbf{#1}}
\newcommand{\me}{\mathrm{e}}
\DeclareMathOperator{\Uniform}{Uniform}
\DeclareMathOperator{\Triangular}{Triangular}
\DeclareMathOperator{\Lognormal}{Lognormal}
\DeclareMathOperator{\BetaPERT}{Beta-PERT}

\newcommand{\labelPrefix}{S}
\renewcommand{\thesection}{\labelPrefix\arabic{section}}
\renewcommand{\theequation}{\labelPrefix\arabic{equation}}
\renewcommand{\thefigure}{\labelPrefix\arabic{figure}}
\renewcommand{\thetable}{\labelPrefix\arabic{table}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\sectionautorefname}{Section}

@@

\begin{document}

\maketitle

We developed a continuous-time, compartmental model consisting of 8
health states (\autoref{model_diag}): susceptible to HIV infection
($S$), vaccinated against HIV ($R$), acute HIV infection ($A$),
undiagnosed HIV infection ($U$), diagnosed but untreated HIV infection
($D$), treated without viral suppression ($T$), viral suppression
($V$), and having AIDS ($W$).  Transitions between states are governed
by a series of differential equations parametrized using rates
estimated from other studies and from incidence and prevalence data
(Table \ref{model_param}).  The model is deterministic, but
uncertainty in the parameters is treated by running the model with
many different samples from the parameter distributions.

\begin{table}
  \begin{center}
    \begin{tabularx}{\textwidth}{lXlll}
      \hline
      & Definition & Value & Reference \\
      \hline
      $\delta$	& Rate of leaving acute infection
      & $\Triangular$(2, 4.14, 9.6)\;y$^{-1}$
      & \cite{Hollingsworth2008-iy} \\
      $\sigma$	& Rate of developing AIDS without viral suppression
      & 0.1064\;y$^{-1}$ & \cite{Morgan2002-cq} \\
      $\theta$ & Rate of developing AIDS with viral suppression
      & See eq.~(\ref{theta}) & --- \\
      $\gamma$ & Rate of viral suppression
      & $\Uniform$(0.5, 1.5)\;y$^{-1}$
      & \cite{Currie2009-yz} \\
      $\nu$ & Death rate from AIDS & 0.5\;y$^{-1}$
      & \cite{Morgan2002-cq} \\
      $\rho$ & Vaccine efficacy & 50\%\,[30\%, 70\%] & --- \\
      $\omega$	& Reduction in lifetime with viral suppression
      & $\Uniform$(5, 8)\;y
      & \cite{Unaids2014-ue, Samji2013-kf} \\
      $\tau_{A}$ & Transmissibility during acute phase
      & $\Triangular$(0.0039, 0.0082, 0.0150)
      & \cite{Skarbinski2015-ni,Wawer2005-us}\\
      $\tau_{U}$ & Transmissibility after acute phase
      & $\Triangular$(0.00077, 0.0014, 0.00251)
      & \cite{Hughes2012-so} \\
      $\varepsilon$ & Relative transmissibility with
      viral suppression & $\BetaPERT$(0.08, 0.002, 0.57)
      & \cite{Donnell2010-xo} \\
      $n$ & Sex acts per year & $\Uniform$(96, 108)
      & \cite{Wawer2005-us,Abdool_Karim2010-cm}\\
      $\mu$ & Background death rate & Country specific
      & \cite{World_Development_Indicators2013-ee} \\
      $B$ & Birth rate & Country specific
      & \cite{World_Development_Indicators2013-ee, WorldBankpg} \\
      $\alpha$ & Diagnosis rate & See eqs.~(\ref{target_rates}) & --- \\
      $\phi$ & Treatment rate & See eqs.~(\ref{target_rates}) & --- \\
      $\psi$ & Rate of relapse to untreated & See eqs.~(\ref{target_rates})
      & --- \\
      $\zeta$ & Vaccination rate & See eqs.~(\ref{target_rates}) & --- \\
      \hline
    \end{tabularx}
    \caption{Model parameters. $\Triangular$, $\Uniform$,
      and $\BetaPERT$ are sampling distributions: see text for a
      full description.  For vaccine efficacy, $50\%$ was the
      baseline, and $30\%$ and $70\%$ were also used in scenario
      analysis.}
    \label{model_param}
  \end{center}
\end{table}

Birth and death.

People living with HIV (PLHIV) are divided among the acutely infected,
undiagnosed, diagnosed, treated, viral suppression and AIDS
compartments. People susceptible to HIV ($S$) progress to the
acute-infection phase ($A$) according to the force of infection
($\lambda$), which depends on the HIV transmission rate, estimated
from the country-specific incidence and prevalence data
(\autoref{model_fitting}), adjusted for the current number of acutely
infected, untreated or ineffectively treated, and viral suppression
PLHIV.  Acute infection is characterized by high viral loads and lasts
an average of 2.90 [95\% confidence interval 1.23, 6.00]\;months
\cite{Hollingsworth2008-iy}.  (We converted these durations to rates
like $1 / 2.90\;\text{month$^{-1}$} \approx 4.14\;\text{y$^{-1}$}$ and
set the parameter using random samples from
$\Triangular(2, 4.14, 9.6)\;\text{y$^{-1}$}$ to capture the
uncertainty in its value.)  We assumed that people remain undiagnosed
during their acute infection phase and during at least some of the
subsequent period of clinical latency (i.e., the undiagnosed
compartment $U$). After acute infection, people move into the chronic
undiagnosed class ($U$).  People in the undiagnosed class will be
diagnosed at the rate $\alpha$, which is determined by the country's
current diagnosis level and its diagnosis target.  Diagnosed people
($D$) transition to the treated compartment ($T$) upon starting ART at
the rate $\phi$, dependent on the country's current treatment level
and its treatment target.  After some time, treated people then to the
viral-suppression class ($V$), at the rate $\gamma$.  We took $\gamma$
as a random sample from $\Uniform(0.5, 1.5)\;\text{y$^{-1}$}$, that
is, viral suppression occurs after between 8 months and 2 years on
treatment \cite{Currie2009-yz}.  The disengagement from treatment
moves people from treated ($T$) and viral suppression ($V$) at the
rate $\psi$, dependent on the current level of viral suppression and
the country's target, back to the diagnosed class ($D$).

PLHIV without viral suppression (compartments $U$, $D$, and $T$)
develop AIDS (compartment $W$) after an average duration of 10.4 y
\cite{Morgan2002-cq}, giving the transition rate
$\sigma = 0.1064\;\text{y$^{-1}$}$.  People who have achieved viral
suppression ($V$) develop AIDS at rate $\theta$, slower than PLHIV
without viral suppression.  People with viral suppression are
estimated to live 5--8 y shorter lives than the non-HIV infected
\cite{Unaids2014-ue, Samji2013-kf}, which we quantified by randomly
sampling the parameter $\omega$ from $\Uniform(5, 8)\;\text{y}$.
Assuming no relapse to untreated, the duration of viral suppression is
\begin{equation}
  \frac{1}{\theta + \mu} = \frac{1}{\mu} - \omega - \frac{1}{\nu}.
\end{equation}
The term to the left of the equals sign is the time until leaving
viral suppression by either progression to AIDS (at rate $\theta$) or
background mortality (at rate $\mu$).  The term to the right of the
equals sign is the lifespan of the non-HIV infected, minus the
reduction in life due to having HIV with viral suppression, minus the
duration of the AIDS stage.  Solving for $\theta$ gives the rate of
progression to AIDS with viral suppression as
\begin{equation}
  \label{theta}
  \theta = \frac{1}{1/\mu - \omega - 1/\nu} - \mu.
\end{equation}

Susceptible people are vaccinated at rate $\zeta$, transitioning into
the vaccinated compartment ($R$), where the vaccine reduces their
force of infection by the efficacy factor $\rho$.

Transition rates between the undiagnosed ($U$), diagnosed ($D$),
treated ($T$), and viral-suppression classes ($V$) are determined by
the proportion of PLHIV diagnosed
\begin{equation}
  p_D = \frac{D + T + V + W}{A + U + D + T + V + W},
\end{equation}
the proportion of diagnosed people on ART
\begin{equation}
  p_T = \frac{T + V + W}{D + T + V + W},
\end{equation}
the proportion of people on ART who have
achieved viral suppression
\begin{equation}
  p_V = \frac{V}{T + V},
\end{equation}
and the proportion of susceptible people vaccinated is
\begin{equation}
  p_R = \frac{R}{S + R}.
\end{equation}

The rates are applied when the proportions of $p_D$, $p_T$, $p_V$, and
$p_R$ are below the target levels:
\begin{equation}
  \label{target_rates}
  \begin{split}
    \alpha(t) &= \alpha_{\max} H\left(p_D^*(t) - p_D(t)\right),
    \\
    \phi(t) &= \phi_{\max} H\left(p_T^*(t) - p_T(t)\right),
    \\
    \psi(t) &= \psi_{\max} H\left(p_V(t) - p_V^*(t)\right),
    \\
    \zeta(t) &= \zeta_{\max} H\left(p^{*}_{R}(t) - p_{W}(t)\right),
  \end{split}
\end{equation}
where $H(x)$ is the Heaviside function
\begin{equation}
  H(x) =
  \begin{cases}
    0 & \text{if $x < 0$},
    \\
    1 & \text{if $x > 0$}.
  \end{cases}
\end{equation}

The model equations are
\begin{equation}
  \label{model_eqns}
  \begin{split}
    \frac{\md S}{\md t} &= B N - \lambda S - \zeta S- \mu S,
    \\
    \frac{\md R}{\md t} & = \zeta S - (1 - \rho) \lambda R - \mu R,
    \\
    \frac{\md A}{\md t} &= \lambda S + (1 - \rho) \lambda R - \delta A - \mu A,
    \\
    \frac{\md U}{\md t} &= \delta A - \alpha U - \mu U - \sigma U,
    \\
    \frac{\md D}{\md t} &=  \alpha U + \psi T + \psi V
    - \phi D - \mu D - \sigma D,
    \\
    \frac{\md T}{\md t} &= \phi D - \psi T - \gamma T - \mu T
    - \sigma T,
    \\
    \frac{\md V}{\md t} &= \gamma T - \psi V - \mu V - \theta V,
    \\
    \frac{\md W}{\md t} &= \sigma U + \sigma D + \sigma T + \theta V -
    \nu W,
  \end{split}
\end{equation}
with force of infection
\begin{equation}
  \label{force_of_infection}
  \begin{split}
    \lambda &= \frac{\beta_A A + \beta_U (U + D + T) + \beta_T V}{N},
    \\
    N &= S + R +  A + U + D + T + V,
    \\
    \beta_x &= T \left[1 - (1 - \tau_x)^n\right]
    \text{ for $x \in \{A, U, T\}$},
    \\
    \tau_T &= \varepsilon \tau_U.
  \end{split}
\end{equation}

$\Uniform(a, b)$ is the uniform random variable with minimum $a$
and maximum $b$: it has density function
\begin{equation}
  \label{uniform}
  p_{\Uniform}(x) =
  \begin{cases}
    \frac{1}{b - a} & \text{if $a \leq x \leq b$,}
    \\
    0 & \text{otherwise.}
  \end{cases}
\end{equation}
We defined the mode for the uniform distribution to be the midpoint
$\frac{b - a}{2}$.
%
$\Triangular(a, b, c)$ is the triangular random variable
distribution with minimum $a$, mode $b$, and maximum $c$: it has
density function
\begin{equation}
  \label{triangular}
  p_{\Triangular}(x) =
  \begin{cases}
    \frac{2 (x - a)}{(c - a)(b - a)} & \text{if $a \leq x \leq b$,}
    \\
    \frac{2 (c - x)}{(c - a)(c - b)} & \text{if $b \leq x \leq c$,}
    \\
    0 & \text{otherwise.}
  \end{cases}
\end{equation}
$\BetaPERT(a, b, c)$ is the beta-PERT probability distribution
\cite{malcom1959} with minimum $a$, mode $b$, and maximum $c$: it has
density function
\begin{equation}
  \label{betaPERT}
  p_{\BetaPERT}(x) =
  \begin{cases}
    \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
    & \text{if $a \leq x \leq c$,}
    \\
    0 & \text{otherwise,}
  \end{cases}
\end{equation}
where
\begin{equation}
  \begin{split}
    \mu &= \frac{a + \lambda b + c}{\lambda + 2},
    \\
    v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
    \\
    w &= \frac{v (a - \mu)}{\mu - c},
  \end{split}
\end{equation}
and $B(v, w)$ is the standard beta function \cite[\S 6.2]{davis1972}.
We used the standard value of $\lambda = 4$.
%
$\Lognormal(\mu, \sigma^2)$ is the lognormal random variable: it has
density function
\begin{equation}
  p_{\Lognormal}(x) = \frac{1}{x \sigma \sqrt{2 \pi}}
  \exp\left(- \frac{\left(\log x - \mu\right)^2}{2 \sigma^2}\right).
\end{equation}

@@

\section{Data sources}
\label{data_sources}

For 127 countries, we found sufficient data to parametrize our model:
these data consisted of estimates of longitudinal HIV incidence and
prevalence for ages 15–49 years starting as early as 1990 in some
countries and running through 2015, along with basic demographics
(\autoref{data_sources}).

@@

@@

Using available historical data for incidence and prevalence, and
published transmission estimates, we estimated transmission rates for
people with acute infection, unsuppressed viral load and suppressed
viral load. Our calibration method provided a recent snapshot of
country-specific transmission, while using historical data to smooth
out variations.

@@

We evaluated the global and country-specific impacts of meeting the
UNAIDS targets and vaccine deployment on four outcome measures: HIV
incidence, PLHIV, number of people with AIDS, and AIDS-related deaths
between 2015 and 2035. Calibrating our model to historical data on
prevalence and incidence, we projected the anticipated trajectories of
the outcomes using country-specific transmission rates across the
intervention scenarios outlined below.  Our base-case scenario assumed
maintenance of the status quo: that 2015 levels of the proportion of
PLHIV diagnosed ($p_{D}$), proportion of those diagnosed on ART
($p_{T}$), and proportion of those on treatment who have achieved
viral suppression ($p_{V}$) continue unchanged until 2035.  The
intervention scenarios were 1.) the attainment of the 90--90--90
target by linear increases in $p_{D}$, $p_{T}$, and $p_{V}$ until 2020
followed by maintenance of those levels until 2035, and 2.) linear
increase in the diagnosis and treatment levels to the 90--90--90
targets by 2020, a linear increase from 90--90--90 to the 95--95--95
target by 2030, and maintenance of the 95--95--95 levels to 2035. (For
90--90--90, if any initial level was above 90\%, it was kept constant
going forward so that the intervention did not worsen coverage.
Likewise, for 95--95--95, any initial level above 95\% was kept
constant.)  For vaccination, we assumed deployment of a vaccine with
50\% efficacy in 2020 with coverage increasing linearly from 0\% to
50\% at 2 years post-rollout and maintaining constant coverage after
reaching 70\%. The added benefit of vaccination was considered in the
context of status quo diagnosis and treatment, achieving the UNAIDS
90–90–90 goal by 2020 followed by maintenance, and achieving the
95–95–95 goal by 2030 followed by maintenance.  Projections were
generated through model simulations based on published parameter
distributions (\autoref{model_param}) and country-specific estimated
transmission rate distributions. The parameters were sampled using
latin hypercube sampling \cite{blower1994} and the variance reduction
technique of running different interventions with random parameter
values \cite{shechter2006}.

@@

We calculated partial rank correlation coefficients (PRCC)
\cite{blower1994} to measure the independent effect of each parameter
on model projections of HIV incidence (\autoref{PRCCs}). Furthermore,
due to uncertainty surrounding the prospective vaccine, we obtained
model projections using six additional vaccine scenarios by
considering alternative estimates of efficacy (30\%, 70\%), coverage
(50\%, 90\%), speed of scale up (10\% coverage per year), and first
year of availability (2025).
